---
title: "Group Assignment 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("readxl")
library(ggplot2)
```

## Load Data

You can include R code in the document as follows:

```{r}
sales <- read_excel("sales-data_clean.xlsx")
sales
```

## Data Exploration

### Add markdown column

```{r}
sales['markdown'] <- NA
for (i in seq(1, nrow(sales), by=15)) {
  j = i+13
  for (k in i:j) {
    if (sales[k, 'Price'] != sales[k+1, 'Price']) {
      sales[k+1, 'markdown'] <- (60 - sales[k+1, 'Price'])/60*100
    }
  }
}
sales
```

### Function: Plot the markdown strategy

```{r}
plot_strategy <- function(data, col, miny, maxy, min_limit, max_limit) {
  vlines <- c()
  for (row in 1:nrow(data)){
    if (!is.na(data$markdown[row])){
      vlines <- append(vlines, data$Week[row])
    }
  }
  p <- ggplot(data, aes_string("Week", col)) + geom_point() +
    geom_point(aes(x=miny, y=maxy)) + xlim(0, 15) + ylim(min_limit, max_limit) +
    geom_vline(xintercept = vlines, color="red", linetype = "dotted") + 
    geom_text(aes(x=vlines, label="Markdown", y=max_limit), colour="red") +
    ggtitle(paste("Item", data$Item[1]))
  p
}
```

### Plot strategy for each item

```{r}
for (i in seq(1, nrow(sales), by=15)) {
  j = i + 14
  print(plot_strategy(sales[i:j,], "Remaining_Inventory", 0, 2000, 0, 2000))
}
```

# Add sales difference column

```{r}
sales['sales_diff'] <- NA
for (i in seq(1, nrow(sales), by=15)) {
  j = i+13
  for (k in i:j) {
    sales[k+1, 'sales_diff'] <- round((sales[k+1, 'Sales'] - sales[k, 'Sales']) / sales[k, 'Sales'], 2)
  }
}
sales
```

### Plot sales difference for each item

```{r}
for (i in seq(1, nrow(sales), by=15)) {
  j = i + 14
  print(plot_strategy(sales[i:j,], "sales_diff", 0, 0, -2.5, 2.5))
}
```

### Function: Calculate the revenue

```{r}
calculate_revenue <- function(data) {
  revenue = 0
  for(row in 1:nrow(data)){
    revenue = revenue + data$Price[row] * data$Sales[row]
  }
  return(revenue)
}
```

### Function: Get strategy

```{r}
strategize <- function(data){
  for (row in 1:nrow(data)){
    if (!is.na(data$markdown[row])) {
      col <- c(data$Item[row], data$Week[row], data$markdown[row], 
               calculate_revenue(data), data$Remaining_Inventory[nrow(data)])
      strategy[nrow(strategy) + 1,] <- col
    }
  }
  return(strategy)
}
```

### Get strategy for each item

```{r}
# add first row to remove later
item <- c(0)
week <- c(0)
markdown <- c(0)
revenue <- c(0)
remaining <- c(0)
strategy <- data.frame(item, week, markdown, revenue, remaining)

for (i in seq(1, nrow(sales), by=15)) {
  j = i + 14
  strategy <- strategize(sales[i:j,])
}

# remove first row
strategy = strategy[-1,]
rownames(strategy) <- 1:nrow(strategy)
strategy
```

### Re-order strategy by decreasing remaining inventory

```{r}
strategy_ordered <- strategy[order(strategy$remaining, decreasing = FALSE),]
strategy_ordered
```


